Response to the reviewers’ comments on the article

### 2020-03-29 article_springer/article_springer.Rmd
Bügele das Englisch

*Proof of Theorem:* We interpret the threshold crossing time $T(\ell)$ as the hitting time of the 
underlying CTRM (Continuous Time Random Maxima) or "max-renewal process", 
and then utilize a result by @MeerschaertStoev08. 
The running maximum process is defined as 
$$
M(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
$$
and since we assumed that the $J_k$ our out of the domain of attraction of a max-stable distribution $F$ (see \eqref{assumptionJs}), there exist 
norming functions $a(c)$ and $d(c)$ such that 
$$
\mathbf P\left[ \frac{M(c) - d(c)}{a(c)} \le \ell^* \right] 
\longrightarrow F(\ell^*), \quad c \to \infty
$$
where $F$ is a generalized extreme value distribution, and $\ell^*$ is any 
value from the support of $F$. 
The CTRM process is then defined via 
$$
V(t) = M(N(t)), \quad t \ge 0
$$
where $N(t)$ is the renewal process associated with the waiting times 
$W_k$: 
$$
N(t) = \max\{n: W_1 + \ldots + W_n \le t\}.
$$
Now a key observation is that
$$
T(\ell) = \inf\{t: V(t) > \ell\}, 
$$
and that

@@

The classical POT approach is based on the fact that exceedances above a high threshold are asymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enough threshold. This approach was well-established a long time ago and is standard in extreme value theory nowadays. Hence we just refer here to the according literature (@smith1984threshold, @leadbetter1991basis, @davison1990models), a nice introduction can be found in @beirlantBook Ch.5.3, @embrechts2013modelling Ch. 6.5. or @ColesBook Ch.4. Hence, we focus in this article mainly on the inter-exceedance times. Due to the Theorem in the last Section we know that for high thresholds the times between exceedances are asymptotically Mittag-Leffler distributed in case of heavy-tailed waiting times between the observations. In this article we propose to proceed with inter-exceedance times in a similar fashion as with the magnitudes in the classical POT approach, more precisely to fit a Mittag-Leffler distribution via stability plots to the inter-exceedance times. Hence, before we talk about inference for the inter-exceedance times in the next section, we first discuss inference for Mittag-Leffler distributions.

@@

Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution. Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator [@hill1975simple] based on the $r+1$ upper order statistics
\begin{align}\label{eq:Hill}
H_{r,n}=\left[ \frac{1}{r} \sum_{i=0}^{r} \log \frac{X_{(i)}}{X_{(r+1)}}\right]^{-1}, 
\end{align}
where $X_{(1)} \geq X_{(2)} \geq \ldots \geq X_{(n)}$ denote the order statistics in decreasing order of a sequence $X_1,\ldots,X_n$. The Hill estimator only performs reliably well for distributions close to Pareto [see @Resnick97]. It heavily depends on the choice of $r$ in \eqref{eq:Hill}, hence on the number of order statistics entering into \eqref{eq:Hill}.  Figure \ref{fig:Hillplots} shows Hill plots for Mittag-Leffler simulated data, with varying sample sizes and tails. To deduce the correct tail parameter estimates from these plots is virtually impossible. To estimate the tail parameter of a Mittag-Leffler distribution with the Hill estimator, the sample size has to be much larger and one has to choose a large tuning parameter $r$. In case that only events above a high threshold are recorded, $n=10000$ events are unrealistic. There is a vast literature on bias-reduced versions of the Hill estimator and on the optimal choice of $r$, mainly based on imposed second-order regular variation conditions [see e.g. @beirlantBook, Ch.4.4 and 4.7 and references in it]. Also, there are lot of other tail-index estimators not taken under consideration in our article, since this would go beyond the scope of our article. However, we know from the Theorem in Section \ref{sec:scaling} that the inter-exceedance times are asymptotically Mittag-Leffler distributed. So all these general tail (and scale) estimation methods are statistically less efficient since they only use a portion of the information contained in the data, as mentioned by @kozubowski2001. Furthermore, the Hill estimator of course completely fails, if the inter-arrival times are exponentially distributed and not heavy-tailed. Hence, we propose to use the log-Moment estimator or the MLE for Mittag-Leffler distributions.

```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 10000 (right), with number of upper order statics r on which the Hill estimator is based on the x-axis. ", out.width = '90%'}
hill_estim<-function(k,data){
  n<-length(data)
  data<-sort(data)
  data_thinned<-data[(n-k):n]
  r<-1/k * sum(log(data_thinned/data_thinned[1]))
  return(1/r)
}

@@

3. Plot $k$ vs.\ $\hat \beta_k$. To the right, as $k \downarrow K_0$, the asymptotics are off and bias is high. To the left (high threshold), data are scarce and variance is high. Choose a region of *stability* in the middle for a parameter estimate $\hat \beta$.

4. Plot $k$ vs.\ $k^{1/\hat \beta} \hat \sigma_k$. Again, choose a region of *stability* as $k$ gets smaller and define $\hat \sigma_0$.

@@

The performance of log-Moment and Maximum-Likelihood estimators for the tail resp. the scale parameter is shown in Figure \ref{Fig:TailSimu} resp. \ref{Fig:ScaleSimu}. Both estimators show good performance, with a slight advantage for the Maximum-Likelihood estimator. This advantage is paid for by a higher computational cost. Moreover, the bottom row in Figure \ref{Fig:TailSimu} shows clearly that the log-Moment and Maximum-Likelihood estimators generalize to the exponential case ($\beta = 1$) whereas a general tail estimator like the Hill-estimator would not.

@@

The bursty CTRE approach to model "non-Poissonian" threshold crossing times should be contrasted with the (now standard) approach of clusters of extremes, see e.g. @ferro2003inference. In this approach, i.i.d. event sequences of magnitudes are generalized to stationary sequences of
event magnitudes (subject to a mixing condition). The two approaches are fundamentally different: A clustering model assumes that each event belongs to one particular (latent) group of events. For bursts, however, the aim is to identify an underlying scale-free pattern in the event 
dynamics, which is often characteristic of complex systems. It is an interesting open problem to develop quality criteria, based e.g. on measures of surprise [@Lee15], which guide an applied statistician in the choice between a clustering and a CTRE approach for a particular problem. But the CTRE approach should not be seen as a substitute for the usual cluster approach. It was for example also observed in @towe2020modelling that clusters of extreme events still exist after declustering. We believe it is possible to unify the cluster approach with our CTRE approach by considering CTREs based on MRPs with a _stationary_, rather than i.i.d., sequence of magnitudes. Then the times between clusters are asymptotically Mittag-Leffler distributed. The identification of clusters in the context of heavy-tailed inter-arrival times is an open problem. But what one could do in case of observing dependencies between the exceedances: one could build natural clusters for example by considering daily maxima instead of hourly maxima.

Finally, a purely scale-free pattern for event times may be too rigid as an 
assumption for some bursty time series, because often the heavy-tailed character of the inter-arrival time
distribution does not hold at all time scales; rather, it applies at short and intermediate time scales, and is truncated (or tempered, 
reverting to an exponential distribution) at very long time scales [see e.g. @MeerschaertRoyQin; and @Aban06]. In such situations, a "tempered" Mittag-Leffler distribution may provide a more realistic fit, which we aim to introduce in follow-up work.

>>>>

*Proof of Theorem:* We interpret the threshold crossing time $T(\ell)$ as the hitting time of the 
underlying CTRM (Continuous Time Random Maxima) or "max-renewal process", 
and then utilize a result by @MeerschaertStoev08. 
The running maximum process is defined as 
$$
M(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
$$
and since the $J_k$ lie in the domain of attraction of a max-stable distribution $F$ (see \eqref{assumptionJs}), there exist 
norming functions $a(c)$ and $d(c)$ such that 
$$
\mathbf P\left[ \frac{M(c) - d(c)}{a(c)} \le \ell^* \right] 
\longrightarrow F(\ell^*), \quad c \to \infty
$$
where $F$ is a generalized extreme value distribution, and $\ell^*$ is any 
value from the support of $F$. 
The CTRM process is then defined via 
$$
V(t) = M(N(t)), \quad t \ge 0
$$
where $N(t)$ is the renewal process associated with the waiting times 
$W_k$: 
$$
N(t) = \max\{n: W_1 + \ldots + W_n \le t\}.
$$
Now a key observation is that
$$
T(\ell) = \inf\{t: V(t) > \ell\}, 
$$
and that

@@

The classical POT approach is based on the fact that exceedances above a high threshold are asymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enough threshold. As this approach is by now well-established in extreme value theory, we do not discuss it any further. Instead, this article focuses on our new contribution: the modelling of inter-exceedance times. For literature pointing to POT see e.g. @smith1984threshold; @leadbetter1991basis; @davison1990models; @beirlantBook Ch.5.3; @embrechts2013modelling Ch. 6.5.; @ColesBook Ch.4.

Due to the Theorem in the last Section we know that for high thresholds the times between exceedances are asymptotically Mittag-Leffler distributed in case of heavy-tailed waiting times between the observations. In this article we propose to model inter-exceedance times in a similar fashion as magnitudes in the classical POT approach, more precisely to fit a Mittag-Leffler distribution to the inter-exceedance times via stability plots. Hence, before we discuss inference for the inter-exceedance times in the next section, we first discuss inference for Mittag-Leffler distributions.

@@

Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution. Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator [@hill1975simple] based on the $r+1$ upper order statistics
\begin{align}\label{eq:Hill}
H_{r,n}=\left[ \frac{1}{r} \sum_{i=0}^{r} \log \frac{X_{(i)}}{X_{(r+1)}}\right]^{-1}, 
\end{align}
where $X_{(1)} \geq X_{(2)} \geq \ldots \geq X_{(n)}$ denote the order statistics in decreasing order of a sequence $X_1,\ldots,X_n$. The Hill estimator only performs reliably well for distributions close to Pareto [see @Resnick97]. It heavily depends on the choice of $r$ in \eqref{eq:Hill}, and hence on the number of order statistics entering \eqref{eq:Hill}.  Figure \ref{fig:Hillplots} shows Hill plots for simulated Mittag-Leffler data, with varying sample sizes and tails. To deduce the correct tail parameter estimates from these plots is virtually impossible. To estimate the tail parameter of a Mittag-Leffler distribution with the Hill estimator, the sample size has to be much larger and one has to choose a large tuning parameter $r$. In case that only events above a high threshold are recorded, $n=10000$ events are unrealistic. There is a vast literature on bias-reduced versions of the Hill estimator and on the optimal choice of $r$, mainly based on imposed second-order regular variation conditions [see e.g. @beirlantBook, Ch.4.4 and 4.7 and references in it]. Also, there are many other tail-index estimators not considered in this article, since this would go beyond the scope of our article. However, we know from the Theorem in Section \ref{sec:scaling} that the inter-exceedance times are asymptotically Mittag-Leffler distributed, and hence it is unsurprising that general tail (and scale) estimation methods that do not take into account this structure are statistically less efficient [@kozubowski2001]. Finally, the Hill estimator completely fails in the important special case where the inter-arrival times are exponentially distributed and not heavy-tailed. For these reasons, we propose to use the log-Moment estimator or the MLE for Mittag-Leffler distributions.

```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 10000 (right), with number of upper order statistics r on which the Hill estimator is based on the x-axis. ", out.width = '90%'}
hill_estim<-function(k,data){
  n<-length(data)
  data<-sort(data)
  data_thinned<-data[(n-k):n]
  r<-1/k * sum(log(data_thinned/data_thinned[1]))
  return(1/r)
}

@@

3. Plot $k$ vs.\ $\hat \beta_k$. To the right ($k \uparrow K$, low threshold), the asymptotics are off and bias is high. To the left ($k \downarrow K_0$, high threshold), data is scarce and variance is high. In the middle, look for a region of *stability* for a parameter estimate $\hat \beta$. Choose as $\hat \beta$ a representative value from this region.

4. Plot $k$ vs.\ $k^{1/\hat \beta} \hat \sigma_k$. Again, choose a region of *stability* and, and choose a representative $\hat \sigma_0$ from that region.

@@

The performance of log-Moment and Maximum-Likelihood estimators for the tail resp. the scale parameter is shown in Figure \ref{Fig:TailSimu} resp. \ref{Fig:ScaleSimu}. Both estimators show good performance, with a slight advantage for the Maximum-Likelihood estimator. This advantage is paid for with a higher computational cost. Moreover, the bottom row in Figure \ref{Fig:TailSimu} shows clearly that the log-Moment and Maximum-Likelihood estimators generalize to the exponential case ($\beta = 1$) whereas the Hill-estimator would not.

@@

The bursty CTRE approach to model "non-Poissonian" threshold crossing times should be contrasted with the (now standard) approach of clusters of extremes, see e.g. @ferro2003inference. In this approach, i.i.d. event sequences of magnitudes are generalized to stationary sequences of
event magnitudes (subject to a mixing condition). The two approaches are fundamentally different: Clustering assumes that each event belongs to one particular (latent) group of events. For bursts, however, the aim is to identify an underlying scale-free pattern in the event 
dynamics, which is often characteristic of complex systems. It is an interesting open problem to develop criteria, based e.g. on measures of surprise [@Lee15], that guide an applied statistician in the choice between a clustering and a CTRE approach for a particular problem. 
In sum, the CTRE approach should not be seen as a substitute for the usual cluster approach, but rather as a complementary approach.

Moreover, it was observed in @towe2020modelling that clusters of extreme events still exist after declustering. We believe it is possible to marry the clustering approach with our CTRE approach by considering CTREs based on MRPs with a _stationary_, rather than i.i.d., sequence of magnitudes, so that the times between clusters are asymptotically Mittag-Leffler distributed. More broadly speaking, the identification of clusters in the context of heavy-tailed inter-arrival times is an open problem.

Finally, a purely scale-free pattern for event times may be too rigid an 
assumption for some bursty time series, because often the heavy-tailed character of the inter-arrival time
distribution does not hold at all time scales. Rather, it applies at short and intermediate time scales, and is truncated (or tempered, 
reverting to an exponential distribution) at very long time scales [see e.g. @MeerschaertRoyQin; and @Aban06]. In such situations, a "tempered" Mittag-Leffler distribution may provide a more realistic fit, which we aim to introduce in follow-up work.

### 2020-03-29 article_springer/changes.Rmd
Bügele das Englisch

* One connection to the Peaks-Over-Threshold (POT) method is, that one has to apply the classical POT approach to the magnitudes. To make this more clear for the reader, we added a comment at the beginning of Section 4. Additionally, inspirited by the POT method, as you said, we propose to fit the inter-exceedance times in a similar fashion: namely, by fitting a Mittag-Leffler distribution to the inter-exceedance times between the peaks over threshold via stability plots. It is true, that the underlying distribution of the magnitudes, in the way we defined the algorithm, gets nearly ignored. A probable extension of our algorithm could be to approximate the tail probability $p_{\ell}$ for very large thresholds by the GPD distribution, which was in a step before fitted to the magnitudes. We add a remark on this after the algorithm.

"The CTRE model considered here can be viewed as a special family of
renewal processes (with power-law waiting times). Their relatively simple
structure makes them amenable to theoretical analysis but for the same rea-
son, I am not convinced that the CTRE model represents a really good
alternative to cluster models as a model for bursty data. The authors' claim
that "visually similar statistical behaviour" can be seen in some real life data
set seems a bit too vague to me."

* The CTRE model is not intended as a substitute for the usual cluster models. It should be more seen as a complement. If there are dependencies in the data, one should first decluster the data. If there are still clusters after (see for example p.3 in @towe2020modelling), the CTRE can maybe account for this behavior. We add a comment on this to the Discussion & Conclusion.

@@

* That is of course true. We calculated here the auto-correlations under the assumption that the underlying data is Mittag-Leffler distributed. The log-Moments of a Mittag-Leffler distribution exist. We added a comment on this in Section 7 to the part "i.i.d.". It is also true that the log-transformation can influence the appearance of the graph. ACFs can always just discover linear dependencies. However, this is just a diagnostic tool to indicate whether the independence assumption is justified. We added for this a comment in the manuscript as well in Section 7 after describing the diagnostic tools.

@@

* It's in interesting idea to use the proposed method for the estimation of the tail index for any power law with $\beta$ < 1. However, this goes beyond the scope of our article. In our article we know from the theory that the inter-exceedance times which we want to model are approximately Mittag-Leffler distributed, hence its natural to use here specific Mittag-Leffler scale and tail estimators.

"The manuscript seems nicely organized. However, writing is not always
precise, the paper contains some typos and not entirely rigorous mathemati-
cal arguments.""

* We revised the whole manuscript according typos, added the missing assumption for the magnitudes and replaced the proof of the theorem by a new, simplified version (EVTL NOCH ANPASSEN).

@@

* You are completely right. This was a typo. We changed this accordingly.

@@

* You are completely right again. This was also a typo. We fixed that.

@@

* TO DO (evtl noch anpassen) We gave a completely new proof. Hence this point no longer applies.

@@

* (EVTL noch anpassen) We added some more explanation to the last two lines.

@@

* For very small tail indices, the (R)MSE is large due to a large variance that results from the fact that in case of a very small tail index single very large events can happen. In the submitted version of the article the simulation study was based on one thousand simulation runs. This was maybe a little bit too small, hence I repeated the study with five thousand runs and now the MSE looks for very small indices more acceptable. I also changed to RMSE since it is easier to interpret.

@@

* You are right. We should better explain this. The plot stabilizes in a region in the middle. We reformulated step 3 accordingly. We also clarified the argument for what was written before at the end of step 4 and added a few sentences for this, following the algorithm.

>>>>

* One connection to the Peaks-Over-Threshold (POT) method is, that one has to apply the classical POT approach to the magnitudes. To make this more clear for the reader, we added a comment at the beginning of Section 4. Additionally, and indeed inspired by the POT method, we propose to fit the inter-exceedance times in a similar fashion: namely, by fitting a Mittag-Leffler distribution to the inter-exceedance times between the peaks over threshold via stability plots. It is true that we largely ignore the underlying distribution of the magnitudes in our algorithm. Our algorithm could potentially be improved by i) fitting a GPD distribution to the exceedances and thus ii) more accurately approximating the tail probability $p_{\ell}$. We mention this idea in a remark following the algorithm.

"The CTRE model considered here can be viewed as a special family of
renewal processes (with power-law waiting times). Their relatively simple
structure makes them amenable to theoretical analysis but for the same reason, I am not convinced that the CTRE model represents a really good
alternative to cluster models as a model for bursty data. The authors' claim
that "visually similar statistical behaviour" can be seen in some real life data
set seems a bit too vague to me."

* The CTRE model is not intended as a substitute for the usual cluster models, but rather as a complement. If there are dependencies in the data, one should first decluster the data. If there are still clusters thereafter (see for example p.3 in @towe2020modelling), the CTRE can possible account for this behavior. We added a comment on this to the Discussion & Conclusion Section.

@@

* This is of course true. We calculated here the auto-correlations under the assumption that the underlying data is Mittag-Leffler distributed. The log-Moments of a Mittag-Leffler distribution exist. We added a comment on this in Section 7 to the part "i.i.d.". It is also true that the log-transformation can influence the appearance of the graph. ACFs only uncover linear dependencies reliably. However, this is just a diagnostic tool to indicate whether the independence assumption is justified. We added a comment on this issue in Section 7 after describing the diagnostic tools.

@@

* It is an interesting idea to use the proposed method for the estimation of the tail index on *any* power law with $\beta$ < 1. However, this goes beyond the scope of our article. In the setting of our article the inter-exceedance times we want to model are approximately Mittag-Leffler distributed, hence it is natural to use specific Mittag-Leffler scale and tail estimators here.

"The manuscript seems nicely organized. However, writing is not always
precise, the paper contains some typos and not entirely rigorous mathematical arguments.""

* We revised the whole manuscript according typos, added the missing assumption for the magnitudes and replaced the proof of the theorem by a new, simplified version.

@@

* We agree and corrected this typographic error.

@@

* This is correct, and we made the change.

@@

* We gave a completely new proof. Hence this point no longer applies.

@@

* We added some more explanation to the last two lines.

@@

* For very small tail indices, the (R)MSE is large due to a large variance that results from the fact that in case of a very small tail index single very large events can happen. In the submitted version of the article the simulation study was based on one thousand simulation runs. This was maybe a little bit too small, hence we repeated the study with five thousand runs and now the MSE looks for very small indices more acceptable. We also changed to RMSE since it is easier to interpret.

@@

* We agree that this should be explained better. The plot stabilizes in a region in the middle. We reformulated step 3 accordingly. We also clarified the argument for what was written before at the end of step 4 and added a few sentences for this, following the algorithm.
